pirouette: Determining the error BEAST2 makes in inferring a phylogeny

### 2019-03-11 article.tex
Process feedback

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{workflow.png}
  \caption{
    \texttt{pirouette} pipeline. 
    The pipeline starts from a true phylogeny (1a) simulated under the selected generative prior $\mathit{P}$, that is converted to an alignment (2a) according to the alignment model $\mathit{A}$. The user supplies one or more experiments. Every experiment $\mathit{X}$ is defined as a combination of an inference model $\mathit{I}$ and the conditions $\mathit{C}$ under which it is actually used in the inference. Based on the experiments and possibly the alignment (2a), experiments are selected to be actually used in the next step (3a).
    Selected experiments use the alignment (2a) and their inference model $\mathit{I}$ to create a BEAST2 posterior of (parameter estimates and) phylogenies (4a). The posterior trees are compared to the true phylogeny (1a) using the selected error measure $\mathit{E}$, in our case the nLTT statistic [\cite{janzen2015approximate}]. Taking the differences between the true tree's nLTT and each posterior's nLTT results in an error distribution, here displayed as a histogram
    of error values (5a). Optionally, a twin phylogeny (1b) can be generated from the true phylogeny (1a), which then results in an error distribution (5b) with similar intermediate steps.
  }
  \label{fig:pipeline}
  \giovanni{
    add reference to the generative prior P (or G) in the figure
  }
  \giovanni{
    I think that a list of possible models should replace the "experiment" 
    cake in the middle, then C should be drawn on the arrow 
    connecting the figure in the middle to 3a. 
    "I" should replace the circled x of passage 3a. 
    An additional C can be drawn alongside the arrow 2a -> 3a. 
    After that a rectangle can be drawn around the whole middle section 
    (including 3a, 3b and the middle C) to denote that this is phase "X".}
  \giovanni{We might also need an arrow going from the central figure to the top arrow (the one with "T") to specify that the twin is generated according to the chosen inference model.}
\end{figure}

@@

\giovanni{This is a slightly more formal version. I personally find it clearer. If you don't like it we can use version 2 (see above in the source). In case you really like it, instead, I can try to make the rest a bit more similar to this.}

@@

\begin{figure}[h]
  \includegraphics[width=\textwidth]{example_5_errors.png}
  \caption{
    Example 5: the error made by BEAST2 from a phylogeny, when the generative model is known, compared to candidates with similar inference models, in relationship to the background error.
    The x-axis specifies the tree type, the y-axis shows the error.
    The boxplot shows the minimum, first quartile, median, third 
    quartile and maximum error, of which the values are displayed 
    in the adjacent label
  }
  \label{fig:example_5}
\end{figure}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{workflow.png}
  \caption{
    \texttt{pirouette} pipeline. 
    The pipeline starts from a true phylogeny (1a) simulated under the selected generative prior $\mathit{P}$, that is converted to an alignment (2a) according to the alignment model $\mathit{A}$. The user supplies one or more experiments. Every experiment $\mathit{X}$ is defined as a combination of an inference model $\mathit{I}$ and the conditions $\mathit{C}$ under which it is actually used in the inference. Based on the experiments and possibly the alignment (2a), experiments are selected to be actually used in the next step (3a).
    Selected experiments use the alignment (2a) and their inference model $\mathit{I}$ to create a BEAST2 posterior of (parameter estimates and) phylogenies (4a). The posterior trees are compared to the true phylogeny (1a) using the selected error measure $\mathit{E}$, in our case the nLTT statistic [\cite{janzen2015approximate}]. Taking the differences between the true tree's nLTT and each posterior's nLTT results in an error distribution, here displayed as a histogram
    of error values (5a). Optionally, a twin phylogeny (1b) can be generated from the true phylogeny (1a), which then results in an error distribution (5b) with similar intermediate steps.
  }
  \label{fig:pipeline}
\end{figure}

@@

\giovanni{
  This is a slightly more formal version. 
  I personally find it clearer. 
  If you don't like it we can use version 2 (see above in the source). 
  In case you really like it, instead, I can try to make the rest a bit more similar to this.
}

@@

\begin{figure}[h]
  \includegraphics[width=\textwidth]{example_5_errors.png}
  \caption{
    Example 5: the error made by BEAST2 from a phylogeny, 
    when the generative model is known, 
    compared to candidates with similar inference models, 
    in relationship to the background error.
  }
  \label{fig:example_5}
\end{figure}
